### 2017-06-20 paper.tex
Know what 'done' looks like (helps close #4)

If lessons are being released regularly,
automate the process.
Old versions of lessons should be archived in a discoverable location for reference.

>>>>

If lessons are being released regularly,
automate the process,
and archive old versions of lessons in a discoverable location for reference.
Also make sure that everyone involved knows what ``done'' look like,
i.e.,
which outstanding issues have to be addressed
and how it has to be formatted
in order for the next release to go out.
A simple checklist stored with the lesson materials is good enough to start,
but as time goes by,
the community may want to use an issue tracking system of some sort
so that work items can be assigned to specific people
and then ticked off as they are completed.
